\documentclass[9.5pt,a4paper]{article} % CHANGED from 10pt to 9.5pt
\usepackage[a4paper,margin=1.1cm]{geometry} % CHANGED margin from 1.2cm to 1.1cm
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\setlength{\columnsep}{0.6cm} % slightly reduced column gap

\definecolor{myblue}{RGB}{0,102,204}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=myblue
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule] % CHANGED \Large to \large

\setlist[itemize]{noitemsep, topsep=0pt, left=1.5em} % MINIMIZE item spacing

\begin{document}

\begin{center}
    {\LARGE \textbf{Vamsikrrishnaa Gangishetty}} \\
    \vspace{0.2em}
    AI Engineer \quad | \quad Full-Stack Developer \quad | \quad Hackathon Winner \\
    \vspace{0.4em}
    \href{mailto:vamsikrrishnaa2004@gmail.com}{vamsikrrishnaa2004@gmail.com} \quad | \quad +91 8331856945 \quad | \quad Hyderabad \\
    \href{https://linkedin.com/in/gangishetty-vamsikrrishnaa}{linkedin.com/in/gangishetty-vamsikrrishnaa} \quad | \quad \href{https://github.com/vamsikrrishnaa}{github.com/vamsikrrishnaa}
\end{center}

\section*{Career Objective}
Innovative and driven Computer Science undergraduate with a strong foundation in Artificial Intelligence, Full-Stack Web Development, and Language Models. Proven experience designing intelligent systems with voice, vision, and reasoning. Passionate about building next-gen AI tools, automating processes, and creating user-first applications for real-world impact.

\section*{Education}
\textbf{B.Tech in Computer Science and Engineering} \hfill \textit{2022 – 2026} \\
Marri Laxman Reddy Institute of Technology and Management \\
\textit{CGPA: 8.00 / 10}

\section*{Highlighted Projects}

\textbf{Voice Assistant (JARVIS Clone)} — \textit{Python, Wikipedia API, Multilingual NLP} \\
An intelligent voice assistant that performs tasks via voice commands, real-time responses, and multilingual NLP.
\begin{itemize}
    \item Executes voice commands to open applications (Chrome, Notepad), websites, and videos.
    \item Multilingual support in Hindi, Telugu, and English via Google Translate and language detection.
    \item Retrieves facts from Wikipedia with contextual parsing and reply generation.
    \item Modular and extensible architecture.
\end{itemize}

\textbf{Retrieval-Augmented Generation (RAG) System} — \textit{Python, LLaMA, Sentence Transformers} \\
Built a semi-automated RAG pipeline for QA using LLMs, web scraping, and semantic filtering.
\begin{itemize}
    \item Scrapes context-rich web sources with BeautifulSoup; filters using sentence similarity.
    \item Powers human-like answers via Mistral/LLaMA with context and time awareness.
    \item Includes prompt rewriter, commonsense fallback, and multi-source logic.
\end{itemize}

\textbf{Journal Website} — \textit{Node.js, Express, MySQL, Passport.js} \\
Secure full-stack journaling platform with session-based access control.
\begin{itemize}
    \item Implements full CRUD via REST APIs; uses EJS for templating.
    \item Handles sessions and password hashing using Passport.js.
    \item Backend designed for modularity and scalability.
\end{itemize}

\textbf{Bounty Dice Game} — \textit{JavaScript, HTML/CSS} \\
Two-player browser dice game featuring animations, scoring, and DOM logic.

\textbf{Guess My Number} — \textit{JavaScript} \\
Logic-based guessing game with interactive feedback and scoring.

\section*{Technical Skills}
\textbf{Languages:} Python, JavaScript, C, HTML, CSS \\
\textbf{Web Technologies:} Node.js, Express.js, REST APIs, EJS, React, Bootstrap \\
\textbf{Databases:} MySQL, SQLite \\
\textbf{Frameworks \& Tools:} Passport.js, Git, VS Code, Postman, Figma \\
\textbf{AI/ML:} LLMs, NLP, Sentence Transformers, pyttsx3 \\
\textbf{Libraries/APIs:} SpeechRecognition, Wikipedia, Googletrans, BeautifulSoup

\section*{Achievements}
\begin{itemize}
    \item \textbf{1st Prize} – National Hackathon on Digital Marketing (Team Lead)
    \item \textbf{3rd Prize} – Smart MECS Hackathon (Among 52 Teams)
\end{itemize}

\section*{Extra-Curricular Activities}
\begin{itemize}
    \item \textbf{Core Member, Tech Club} – Led 3+ technical and non-technical events
    \item \textbf{Peer Mentor} – Guided juniors in AI, web development, and system design
\end{itemize}

\end{document}
